\documentclass[11pt, a4paper]{moderncv}
\moderncvtheme[black]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage[sfdefault, lf]{carlito}
\usepackage[rmdefault]{libertinus}
\usepackage{paracol}
\usepackage{environ}

\newcommand{\firstcolumn}{0.50}
\newcommand{\secondcolumn}{0.48}
\newcommand{\spacing}{\vspace{3pt}}
\newcommand{\subspacing}{\vspace{1pt}}

\renewcommand{\titlefont}{\huge \bfseries \rmfamily \color{color1}}
\renewcommand{\sectionfont}{\Large \bfseries \rmfamily}
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{B}{>{\bfseries}l}
\newcolumntype{S}{@{\hskip 1em} }

\newcommand*{\entry}[3]{
	\textbf{#1} \subsectionrule \textit{#2}
	\ifx
		\relax#3\relax
		\par
	\else
		\begin{itemize}
		#3
		\end{itemize}
	\fi
	\subspacing
}

\NewEnviron{entrytable}{
	\begin{tabularx}{\linewidth}{@{} B S X @{}}
        \BODY
	\end{tabularx}
}

\begin{document}
	{\titlefont Teddy Wachtler} \sectionrule
	\par \spacing
	\begin{tabularx}{\textwidth}{L L L}
		\textit{Postal:} 3058 N Rockmont Ave \par
		\phantom{\textit{Postal:}} Claremont, CA, 91711 &
		\textit{Email:} \emaillink{thwamster@gmail.com} \par
		\textit{Email:} \emaillink{thwachtler@willamette.edu} &
		\textit{Phone:} +1--909--407--1640 \par
		\textit{Site:} \href{https://thwamster.github.io/}{thwamster.github.io} \\
	\end{tabularx}

	\spacing

	\begin{minipage}[t]{\firstcolumn \textwidth}

		\section{Education} \label{sec:education}
		\entry{Willamette University}{Present}{
			\item B.A., Politics, Policy, Law, \& Ethics. GPA: 4.00.
			\item Served on the executive board of 3 student organizations.
		}
		\entry{Damien High School}{Aug. 2021--May 2025}{
			\item Valedictorian, Junior of the Year, AP Scholar with Distinction, and NMSC commended student. GPA: 4.55 (3.98 u.).
			\item Certificates of outstanding achievement in 18 classes.
			\item Participated in the Project Lead the Way Engineering and Computer Science programs.
		}

		\section{Extracurriculars} \label{sec:extracurriculars}
		\entry{British Parliamentary Debate}{Aug. 2025--Present}{
			\item Debate Union Treasurer; Managed a \$3,000 budget and coordinated expenditures across registration, travel, and other forensic events.
			\item Competed in local and national circuits, accumulating multiple finals placements and speaker awards.
		}
		\entry{Policy Debate}{Aug. 2021--Apr. 2025}{
			\item Varsity letter and team captain; Constructed numerous research-based defenses of policy and critical propositions.
			\item Competed on the national circuit with numerous deep tournament runs and qualified to the Tournament of Champions twice.
		}
		\entry{Model United Nations Club}{Aug. 2025--Present}{
			\item Treasurer; Organized the hosting of multiple conferences.
		}
		\entry{Mock Trial}{Sep. 2023--Dec. 2024}{
			\item Team captain, club Vice President, lead pre-trial attorney, and primary student organizer.
		}
		\entry{Scouting America}{Jul. 2018--May 2025}{
			\item Troop 403; Eagle Scout (Board of Review pending). \item Project consisted of significant landscaping, woodworking, and repair efforts at a children's center over 130 hours.
			\item Led classes for youth aged 11--17 in domestic and national politics, fitness, communication, environmental science, and metalworking.
		}
		\entry{Robotics}{Aug. 2024--Jan. 2025}{
			\item Lead coder for national-circuit VEX V5 competition.
		}
		\entry{Christian Leadership}{Aug. 2024--May 2025}{
			\item Led religious retreats for peers with a strong emphasis on community-building and spiritual growth.
		}
		\entry{Dungeons and Dragons Club}{Oct. 2021--Present}{
			\item President in H.S. and Treasurer in college.
		}
		\entry{Ultimate Frisbee Club}{Oct. 2023--Oct. 2024}{
			\item Secretary; Managed communication and statistics.
		}
		\entry{Stagecraft}{Jan. 2026--Present}{}
		\entry{Road Cycling Club}{Aug. 2021--Dec. 2022}{}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{\secondcolumn \textwidth}
		\section{Summary} \label{sec:summary}
		\textit{Interdisciplinary student and researcher actively engaged in competitive academic discourse, data-driven technical and policy research, and community service.}

		\section{Research \& Programs} \label{sec:research}
		\entry{Computing Research Association}{Feb. 2026--Present}{
			\item Contracted researcher in the CRA UR2PhD REU program.
			\item Explored the application of machine learning algorithms to the opioid epidemic through a spatio-temporal perspective.
			\item Developing a predictive model to classify overdose risk rates based on the SDoH.
		}
		\entry{Univ. of Michigan Debate Institute}{Jun. 2023--Jul. 2023}{
			\item Studied fiscal redistribution and solutions to income inequality with targeted research on the expansion of SSI to U.S. territories and the adoption of a FJG in the executive branch.
		}
		\entry{Gonzaga Univ. Debate Institute}{Jun. 2022--Jul. 2022}{
			\item Analyzed U.S.-NATO security cooperation over emerging technologies, specifically regarding integrating machine learning in military and scientific technology and combating disinformation with cybersecurity techniques.
		}

		\section{Project Examples} \label{sec:projects}
		\entry{QEMU RISC-V Operating System}{Jan. 2026--Present}{
			\item Building a bare-metal O.S. in C for RISC-V architecture with dynamic memory allocation, error handling with runtime symbol resolution, and an interactive terminal.
		}
		\entry{Brick Classifier Prototype}{Aug. 2024--May 2025}{
			\item Designed and prototyped an automated LEGO sorter machine with a Java host communicating over SSH with an RPI, a VEX V5 brain, and a gRPC server for real-time classification and motor movement.
		}
		\entry{Evolutionary Algorithm Sim.}{Jan. 2025--Mar. 2025}{
			\item Designed and built a C\# genetic algorithm in Unity to complete a simulated game through mutation.
		}

		\section{Skills} \label{sec:skills}
		\begin{entrytable}
			Languages & Java, C\#, Rust, C, C++, LaTeX \\
			Software & Git, Vim, Unity, CMake, Fusion360, LVGL \\
			Platforms & Windows, Linux (Arch), MS Office, Google Workspace, Raspberry Pi \\
			Engineering & CAD modeling, technical drawing, embedded systems, 3D printing \\
			Applied & Landscaping, woodworking, construction,  maintenance work
		\end{entrytable}

	\end{minipage}
\end{document}
